Transfer Learning in Visual and Relational Reasoning

### 2020-02-07 Transfer_Learning/cvpr_2nd_submission/experiments.tex
Small edits in Experiments & Transfer Learning sections.

For the CLEVR dataset, we consider the 5 question categories defined by the authors: \textit{Exist}, \textit{Count}, \textit{CompareInteger}, \textit{CompareAttribute}, \textit{QueryAttribute}. We also consider the CoGenT (Constrained Generalization Test) variant of CLEVR which contains 2 conditions, differing by the available combinations of 8 object color-attributes. The colors are partitioned into two complementary families:
Gray, Blue, Brown and Yellow in \textbf{Family A} and Red, Green, Purple, Cyan in \textbf{Family B}.
The cubes and cylinders take colors from complementary families in each variant with opposite configurations while the spheres can take any color (See~\cref{tab:cogent_conditions}).
As the input domain consist of the set of objects with all attribute values, both variants differ by their marginal distributions $P_S$ and $P_T$.

We compare SAMNet's performance to several models: Transparency by Design networks (TbD)~\cite{mascharka2018transparency}, Feature-wise Linear Modulation (FiLM)~\cite{perez2018film} and the Program Generator + Execution Engine (PG + EE), presented in \cite{johnson2017inferring}. For performance reasons, we deactivated the external memory and temporally-related modules in SAMNet as they are unnecessary while reasoning about static images.
Results are shown in \cref{fig:clevr-baseline-compare}. \vm{Not sure what else to say here..}

\begin{figure}[!t]
	\centering
	\includegraphics[width=\columnwidth]{../results/CLEVR_baselines_comparison.pdf}
	\caption{Comparison of SAMNet to baseline models~\cite{mascharka2018transparency, perez2018film, johnson2017inferring} on CLEVR.}
	\label{fig:clevr-baseline-compare}
\end{figure}

>>>>

For CLEVR, we consider the 5 question categories defined by the authors: \textit{Exist}, \textit{Count}, \textit{CompareInteger}, \textit{CompareAttribute}, \textit{QueryAttribute}. We also consider the CoGenT (Constrained Generalization Test) variant of CLEVR which contains 2 conditions, differing by the available combinations of 8 object color-attributes. The colors are partitioned into two complementary families:
Gray, Blue, Brown and Yellow in \textbf{Family A} and Red, Green, Purple, Cyan in \textbf{Family B}.
The cubes and cylinders take colors from complementary families in each variant with opposite configurations while the spheres can take any color (See~\cref{tab:cogent_conditions}).
As the input domain consist of the set of objects with all attribute values, both variants differ by their marginal distributions $P_S$ and $P_T$.

We compare SAMNet's performance to several models: Transparency by Design networks (TbD)~\cite{mascharka2018transparency}, Feature-wise Linear Modulation (FiLM)~\cite{perez2018film} and the Program Generator + Execution Engine (PG + EE), presented in \cite{johnson2017inferring}. For performance reasons, we deactivated the external memory and temporally-related modules in SAMNet as they are unnecessary while reasoning about static images. SAMNet reaches 96.2\% accuracy on CLEVR, compared to 96.9\%, 97.7\% and 98.7\% for PG + EE, FiLM and TbD respectively.

% \begin{figure}[!t]
% 	\centering
% 	\includegraphics[width=\columnwidth]{../results/CLEVR_baselines_comparison.pdf}
% 	\caption{Comparison of SAMNet to baseline models~\cite{mascharka2018transparency, perez2018film, johnson2017inferring} on CLEVR.}
% 	\label{fig:clevr-baseline-compare}
% \end{figure}

### 2020-02-07 Transfer_Learning/cvpr_2nd_submission/transfer_learning.tex
Rewrite Experiments section and add back Summary.
Small edits in Experiments & Transfer Learning sections.

\section{Transfer Learning}

\begin{figure*}
	\centering
	\includegraphics[width=0.9\textwidth]{../img/architecture/transfer_taxo}
	\caption{Transfer learning taxonomy.}\label{fig:taskonomy}
\end{figure*}
Due to the complex nature of visual reasoning, it appears that
transfer learning from a source domain to a target domain can be investigated in
multiple ways, depending on how the features are related between the two domains. This includes attributes such as size, color and shape, as well as temporal characteristics reflected in the number of frames and the scene complexity.
To establish a formal framework for these various aspects, we first recall the basic definition of transfer learning~\cite{pan2009survey}.

@@

We now formally define 3 kinds of transfer learning problems, namely,
\emph{feature transfer}, \emph{temporal transfer},
and \emph{reasoning transfer}.
These are illustrated in~\cref{fig:taskonomy} using representative examples from CLEVR-CoGenT and COG datasets that are particularly suited for experimental
investigations of transfer learning.
In the next section we detail the performance of
SAMNet for each of these 3 kinds, using the CLEVR-CoGenT dataset
for feature transfer, the COG dataset for temporal transfer, and finally
both datasets for reasoning transfer, with appropriate baseline comparisons.

>>>>

\section{Transfer Learning}
\label{sec:transfer_learning}
\begin{figure*}
	\centering
	\includegraphics[width=0.9\textwidth]{../img/architecture/transfer_taxo}
	\caption{Transfer learning taxonomy.}\label{fig:taskonomy}
\end{figure*}
Due to the complex nature of visual reasoning, it appears that
transfer learning from a source domain to a target domain can be investigated in
multiple ways, depending on how the features are related between the two domains. This includes attributes such as size, color and shape, as well as temporal characteristics reflected in the number of frames and the scene complexity.
To establish a formal framework for these various aspects, we first recall the basic definition of transfer learning~\cite{pan2009survey}.

@@

We now formally define 3 kinds of transfer learning problems, namely,
\emph{feature transfer}, \emph{temporal transfer},
and \emph{reasoning transfer}.
These are illustrated in~\cref{fig:taskonomy} using representative examples from CLEVR-CoGenT and COG datasets that are particularly suited for experimental
investigations of transfer learning.
In \cref{sec:experiments}, we detail the performance of
SAMNet for each of these 3 kinds, using the CLEVR-CoGenT dataset
for feature transfer, the COG dataset for temporal transfer, and finally
both datasets for reasoning transfer, with appropriate baseline comparisons.
